Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-05-22 ms.tex
Add marginal posterior

>>>>

In Bayesian inference, although it is often easy to write down the likelihood or even the full posterior in closed form, usually one is interested in only a subset $\boldsymbol\beta$ of all of the model's parameters, the others $\boldsymbol\lambda$ being nuisance parameters. In this case, we integrate away the nuisance parameters, forming the marginal posterior
%
\begin{equation}\label{eq:marginal-posterior}
	p(\boldsymbol\beta|\mathbf X) = \int \frac{p(\mathbf X|\boldsymbol\beta,\boldsymbol\lambda) p(\boldsymbol\beta,\boldsymbol\lambda)}{p(\mathbf X)} \,\mathrm{d}\boldsymbol\lambda
\end{equation}
%
with $\boldsymbol\theta = (\boldsymbol\beta, \boldsymbol\lambda)$. For instance, for the purpose of locating a \ac{GW} source on the sky, all parameters but $(\alpha, \delta)$ are nuisance parameters.
